---
title: "BSMM-lab-2"
subtitle: "BSMM 8740 Fall 2023"
author: "Masrura Tamanna"
date: "25/09/2023"
format: html
editor: visual
self-contained: true
---

## Setup

Load packages and data:

```{r load-pkg-data}
#| message: false
the_tate <- readr::read_delim("data/the-tate-collection.csv", ";", escape_double = FALSE, trim_ws = TRUE)
the_tate_artists <- readr::read_csv("data/the-tate-artists.csv")
```

## Exercises

### Exercise 1

```{r}
the_tate |> dplyr::summarize(
  artist=length(unique(artist)),
  min_year=min(year,na.rm =TRUE),
  max_year=max(year,na.rm = TRUE),
  min_acquisitionYear=min(acquisitionYear,na.rm=TRUE),
  max_acquisitionYear=max(acquisitionYear,na.rm=TRUE),
)
```

```{r}
the_tate |> DataExplorer::introduce()
```

```{r}
the_tate |> DataExplorer::plot_missing()
```

The `the_tate` data-set has 3532 unique artists who worked from \_\_\_ to \_\_\_. The works were acquired between the years \_\_\_ and \_\_\_.

### Exercise 2

```{r}
the_tate |> dplyr::filter(is.na(year)) |> dplyr::distinct(artist)
```

```{r}
the_tate |> dplyr::filter(is.na(year)) |> dplyr::distinct(title)
```

```{r}
the_tate |> dplyr::filter(is.na(year))

table(qaz$artist) |> tibble::tibble()
```

How number of works with missing dates is \_\_.

The number of artists whose works have missing dates is \_\_.

It would require resolving missing year data for only \_\_ artists resolve resolve at least 50% of the missing data.

The missing year data likely to be classified as \_\_\_\_.

### Exercise 3

```{r}
the_tate |> dplyr::group_by(artist) |>
dplyr::mutate(n=n()) |>
  dplyr::select(artist,n) |> 
  dplyr::arrange(desc(n)) |>
  dplyr::distinct() |> 
  dplyr::ungroup() |> 
  dplyr::slice(c(1,10))
```

The artist with the most works in the Tate collection is \_\_\_.

The artist with the tenth-most works in the Tate collection is \_\_\_.

### Exercise 4

```{r}
the_tate |> dplyr::group_by(artist) |>
dplyr::mutate(n=n()) |>
  dplyr::select(artist,n) |> 
  dplyr::arrange(desc(n)) |>
  dplyr::distinct() |> 
  dplyr::ungroup() |> 
  dplyr::mutate(
    total=sum(n),
    pct=n/total
  )
```

The artist with the greatest number of works in the Tate collection represent \_\_\_% of the total number of works

### Exercise 5

There are \_\_ duplicate artist-title pairs

### Exercise 6

The artist with the largest work in the tate collection is \_\_\_

The artist with the smallest work in the collection is \_\_\_. The smallest work has area \_\_\_ $\text{cm}^2$

### Exercise 7

...

### Exercise 8

The annual return in the SPX price in 2020 was \_\_\_%.

The corresponding price volatility was \_\_\_%.

### Exercise 9

The period volatility was \_\_\_.\_%

### 
